\texttt{MSnbase}, efficient R-based processing and visualisation of raw mass spectrometry data

### 2020-04-28 msnbase2.tex

\begin{abstract} %% 200 words max
  We present version 2 of the \texttt{MSnbase} R/Bioconductor
  package. \texttt{MSnbase} provides infrastructure for the
  manipulation, processing and visualisation of mass spectrometry
  data. Here we present how the new \textit{on-disk} infrastructure
  allows the handling of hundreds on commodity hardware and present
  some application of the package.
\end{abstract}

@@

As is custom with Bioconductor packages, \texttt{MSnbase} comes with
ample documentation. Every user-accessible function is documented in a
dedicated manual page. In addition, the package offers 5 vignettes,
including one aimed at developers. Question from users and developers
are answered on the Bioconductor support forum as well as on the
package GitHub page. The package provides several sample and
benchmarking datasets, and relies on other dedicated
\textit{experiment packages} such as \texttt{msdata}~\cite{msdata} for
raw data or \texttt{pRolocdata}~\cite{Gatto:2014a} for quantiative
data. \texttt{MSnbase} is available on Windows, Mac OS and Linux under
the open source Artistic 2.0 license and easily installable using
standard installation procedures.

The version of \texttt{MSnbase} used in this manuscript is
2.13.9. The main features presented here were available since
version 2.0.

>>>>

\begin{abstract} %% 200 words max
  We present version 2 of the \texttt{MSnbase} R/Bioconductor
  package. \texttt{MSnbase} provides infrastructure for the
  manipulation, processing and visualisation of mass spectrometry
  data. We focus on the new \textit{on-disk} infrastructure, that
  allows the handling of large raw mass spectrometry experiment on
  commodity hardware and illustrate how the package is used for data
  processing, method development and visualisation.
\end{abstract}

@@

As is custom with Bioconductor packages, \texttt{MSnbase} comes with
ample documentation. Every user-accessible function is documented in a
dedicated manual page. In addition, the package offers 5 vignettes,
including one aimed at developers. Questions from users and developers
are answered on the Bioconductor support forum as well as on the
package GitHub page. The package provides several sample and
benchmarking datasets, and relies on other dedicated
\textit{experiment packages} such as \texttt{msdata}~\cite{msdata} for
raw data or \texttt{pRolocdata}~\cite{Gatto:2014a} for quantiative
data. \texttt{MSnbase} is available on Windows, Mac OS and Linux under
the open source Artistic 2.0 license and easily installable using
standard installation procedures.

The version of \texttt{MSnbase} used in this manuscript is
2.13.9. The main features presented here were available since
version 2.0. The code to reproduce the analyses and figures in this
article is available at
\url{https://github.com/lgatto/2020-msnbase-v2/}.
